Dynamical Properties of Molecular Cloud Complexes in a Redshift 6 Prototypical Galaxy at the Epoch of Reionization

### 2018-09-08 WRITEUP/ms.tex
write some more

\begin{figure*}[htbp]
\centering
\includegraphics[trim=0 0 0 0, clip, width=0.85\textwidth]{\figpath/ss16_alphavir.png}
\includegraphics[trim=0 0 0 0, clip, width=0.85\textwidth]{\figpath/ss16_PVE.png}
\caption{
Top: Virial parameter and cloud mass of \flower of a given snapshot (accreting phase).
Bottom: $\sigma^2/R - \Sigma_{\rm gas}$ relation of MCs in the same snapshot.
The V-shaped dashed lines show locii along which the given external pressures
are needed in order for MCs to have linewidth $\sigma$ for a given set of surface densities. (see \Sec{PVE})
\label{fig:alpha16}}
\end{figure*}

\begin{figure*}[htbp]
\centering
\includegraphics[trim=0 0 0 0, clip, width=0.85\textwidth]{\figpath/ss27_alphavir.png}
\includegraphics[trim=0 0 0 0, clip, width=0.85\textwidth]{\figpath/ss27_PVE.png}
\caption{
Top: Virial parameter and cloud mass of \flower of a given snapshot (starburst phase).
Bottom: $\sigma^2/R - \Sigma_{\rm gas}$ relation of MCs in the same snapshot.
\label{fig:alpha27}}
\end{figure*}

@@

\begin{figure*}[htbp]
\centering
\includegraphics[trim=0 0 0 0, clip, width=0.85\textwidth]{\figpath/ss16-28_alphavir.png}
\includegraphics[trim=0 0 0 0, clip, width=0.85\textwidth]{\figpath/ss16-28_PVE.png}
\caption{
Top: Virial parameter and cloud mass of MCs in \flower identified across all snapshots.
Bottom: $\sigma^2/R - \Sigma_{\rm gas}$ relation of MCs.
\label{fig:alpha16-28}}
\end{figure*}

@@

The range of masses of the MCs identified are consistent with the mass range observed in \z$\sim$2 galaxies in $i$-band light (rest-frame visible),
between $M_{\rm cl}\approx$10$^{7-9}$\,\Msun \citep{Elmegreen07a, Elmegreen09a}.

Noisy due to resolution effect, since we only have one galaxy here. However,
we could improve the ``signal-to-noise'' ratio by including clouds identified from different
snapshots\footnote{This approach is valid unless in some snapshots,
the galaxy experience a violent event, which is relatively rare across the few 100\,Myr studied here.}.
We fit a power-law to the cumulative mass function (CMF), expressed in the form of 
\begin{equation}
n\left(M^\prime > M\right) \propto M_{\rm cl}^\alpha,
\end{equation}
where $n$ is the number of MCs with masses exceeding $M_{\rm cl}$ and $\alpha$ is the power-law index.
The slope varies from $-$0.49\pmm0.01 to $-$1.17\pmm0.06 for MCs identified using the lowest and the
highest $n_{\rm cut}$ adopted in this study.
The uncertainties here are the formal fitting uncertainties.
Regardless of the density threshold adopted, the slope of the CMF of \flower (\Fig{cmf})
is shallower compared to those observed in nearby galaxies (between $-$1.6 and $-$2.5; based on a sample of
$\sim$70 resolved GMCs in M31, M33, IC10 and the Magellanic Clouds; \citealt{Blitz07a}). % between -1.6 to -2.5, mostly -1.7, except for M33, which is -2.5

@@

\AP{This would be something like \quotes{origin of the cloud and implication of the found properties} if we put there toomre and CMF}

Yet.... at the epoch of reionization.... For instance, to resolve the
\aco line emission in a $L^*$ prototypical galaxy at \z$\sim$6 on xxx\,pc
require .... on-source time even with ALMA.

Connection to observations

@@

Looking at correlations between physical parameters such as xx, yy, zz and the CMF
can provide valuable information for developing models of \SF at EoR and
galaxy evolution.

@@

%--------------------------------------------------------------------------
%                                Conclusions
%--------------------------------------------------------------------------
\section{Summary and Conclusions}      \label{sec:conclusion}

We study the dynamical properties of molecular complexes in a \z$\sim$6 lyman-break galaxy,
at the end of the epoch of reionization using state-of-the-art cosmological zoom-in simulation
(\ncode{Serra}). We identify molecular cloud complexes in the main galaxy of the
simulated 20\,Mpc h\pmOne box (aka \flower; \citealt{Pallottini17a}) using a method analogues
to the kd-tree idea. We decompose the molecular structures into non-overlapping tiles
% (stored in a kd-tree)
by identifying a set of different density contours at different snapshots.
Using volumetric H$_2$ is essentially the same as identified molecular structures using
different contours in line emission (e.g., CO, CS, NH$_3$)
% and different molecular line tracers trace different MCs on different scales due to their
% different critical densities.
since the line luminosity scales with the molecular gas density.
Our simulations include the effect of feedback from .... .and ....., which are the main source
of non-thermal pressure ejected into the ISM.
We examine the properties of the complexes' at different evolutionary stages and compare
them with nearby and \highz observations. In particular,
the scaling relations between velocity dispersion, complex size, gas mass,
and SFRs.

@@

Determining the multi-phase ISM properties of early galaxies
is a critical piece to understanding the evolution and
assembly history of galaxies, since they set the pace
for chemical reactions and excitation rates for the coolants in the ISM (and subsequent star formation).
Observations leveraging the combination of spatio-spectral imaging of
multi-band continuum and spectral line emission are crucial for better understanding
the role of \highz galaxy populations
(e.g., LBGs, BzKs, and DSFGs) in
galaxy evolution and the ISM physics behind their intense star formation in the early universe
(if only the ALMA TAC will give us to the time to do so)...

@@

\appendix
\section{Schmidt-Kennicutt Relation}
As benchmarking, we check the SK relation of the MCs identified based on their SFR and gas surface densities.
We show in \Fig{sk} the MCs of \flower, identified using different $n_{\rm cut}$ in the ``accreting snapshot'' 
(see \Sec{sfh} for details) compared to those reported in \obs.

@@

\AP{I would put a figure with the SK-relation for the clumps in a single snapshot for different cuts, along with the observed points and the global \flower point from the data found in \citet{Pallottini17b}}
\DL{to do... after getting points from Pallo, then update plot\_cloud\_prop.py and plotsingleSS.py (uncomment plot\_suff(SK) and only plot snapshot 16)}

\begin{figure*}[htbp]
\centering
\includegraphics[trim=0 0 0 0, clip, width=0.85\textwidth]{\figpath/}
\caption{
SFR and gas surface densities of MCs identified in \flower in \ncode{serra} (xxx symbol) compared to those 
observed in 0$\lesssim$\,\z$\lesssim$2 galaxies (xxx symbol). 
The literature data are compiled from \citealt{Leroy13a, Genzel13a, Sharon13a, Hodge15a}, \citealt{Pallottini17b} and references therein, and Sharon et al. in prep.
\label{fig:sk}}
\end{figure*}

>>>>

\begin{figure*}[htbp]
\centering
\includegraphics[trim=0 0 0 0, clip, width=0.85\textwidth]{\figpath/ss16_alphavir.png}
\includegraphics[trim=0 0 0 0, clip, width=0.85\textwidth]{\figpath/ss16_PVE.png}
\caption{
Top: Virial parameter and cloud mass of \flower in the accreting phase (star symbols) compared to those observed in the Milky Way.
Literature data are compiled from \citealt{Kauffmann17b} and references therein.
Bottom: $\sigma^2/R - \Sigma_{\rm gas}$ relation of the MCs (star symbols) 
compared to those observed in the Milky Way (black dot markers).
The V-shaped dashed lines show locii along which the given external pressures
are needed in order for MCs to have linewidth $\sigma$ for a given set of surface densities. (see \Sec{PVE})
In both panels, the star symbols are color-coded by the $n_{\rm cut}$ adopted to identify the corresponding MCs.
\label{fig:alpha16}}
\end{figure*}

\begin{figure*}[htbp]
\centering
\includegraphics[trim=0 0 0 0, clip, width=0.85\textwidth]{\figpath/ss27_alphavir.png}
\includegraphics[trim=0 0 0 0, clip, width=0.85\textwidth]{\figpath/ss27_PVE.png}
\caption{
Same as \Fig{alpha16}, but for MCs identified in the starburst phase of \flower.
\label{fig:alpha27}}
\end{figure*}

@@

\begin{figure*}[htbp]
\centering
\includegraphics[trim=0 0 0 0, clip, width=0.85\textwidth]{\figpath/ss16-28_alphavir.png}
\includegraphics[trim=0 0 0 0, clip, width=0.85\textwidth]{\figpath/ss16-28_PVE.png}
\caption{
Same as \Fig{alpha16}, but for MCs identified across all snapshots. 
Star symbols are color-coded by increasing SFR.
\label{fig:alpha16-28}}
\end{figure*}

@@

The range of masses of the MCs identified are consistent with the mass range observed in \z$\sim$2 galaxies in $i$-band 
(i.e., rest-frame visible) which is between $M_{\rm cl}\approx$10$^{6.5-9}$\,\Msun \citep{Elmegreen07a, Elmegreen09a}.
Observational studies.. the ... distribution as the cumulative mass function (CMF).
Noisy due to resolution effect, since we only have one galaxy here. However,
we could improve the ``signal-to-noise'' ratio by including clouds identified from different
snapshots\footnote{This approach is valid unless in some snapshots,
the galaxy experience a violent event, which is relatively rare across the few 100\,Myr studied here.}.
We fit a power-law to the CMF, expressed in the form of 
\begin{equation}
n\left(M^\prime > M\right) \propto M_{\rm cl}^\alpha,
\end{equation}
where $n$ is the number of MCs with masses exceeding $M_{\rm cl}$ and $\alpha$ is the power-law index.
The slope varies from $-$0.49\pmm0.01 to $-$1.17\pmm0.06 for MCs identified using the lowest and the
highest $n_{\rm cut}$ adopted in this study.
The uncertainties here are the formal fitting uncertainties.
Regardless of the density threshold adopted, the slope of the CMF of \flower (\Fig{cmf})
is shallower compared to those observed in nearby galaxies (between $-$1.6 and $-$2.5; based on a sample of
$\sim$70 resolved GMCs in M31, M33, IC10 and the Magellanic Clouds; \citealt{Blitz07a}). % between -1.6 to -2.5, mostly -1.7, except for M33, which is -2.5

@@

\AP{This would be something like \quotes{origin of the cloud and implication of the found properties} if we put there toomre and CMF}
\DL{maybe just merge in the previous sections when we present the results?}

Yet.... at the epoch of reionization.... For instance, to resolve the
\aco line emission in a $L^*$ prototypical galaxy at \z$\sim$6 on xxx\,pc
require .... on-source time even with ALMA.
ngVLA

@@

@@

%--------------------------------------------------------------------------
%                                Conclusions
%--------------------------------------------------------------------------
\section{Summary and Conclusions}      \label{sec:conclusion}
Looking at correlations between physical parameters such as xx, yy, zz and the CMF
can provide valuable information for developing models of \SF at EoR and
galaxy evolution.

We study the dynamical properties of molecular complexes in a \z$\sim$6 lyman-break galaxy,
at the end of the epoch of reionization using state-of-the-art cosmological zoom-in simulation
(\ncode{Serra}). We identify molecular cloud complexes in the main galaxy of the
simulated 20\,Mpc h\pmOne box (aka \flower; \citealt{Pallottini17a}) using a method analogues
to the kd-tree idea. We decompose the molecular structures into non-overlapping tiles
by identifying a set of different density contours at different snapshots.
Using volumetric H$_2$ is essentially the same as identified molecular structures using
different contours in line emission (e.g., CO, CS, NH$_3$)
% and different molecular line tracers trace different MCs on different scales due to their
% different critical densities.
since the line luminosity scales with the molecular gas density.
Our simulations include the effect of feedback from .... .and ....., which are the main source
of non-thermal pressure ejected into the ISM.
We examine the properties of the complexes' at different evolutionary stages and compare
them with nearby and \highz observations. In particular,
the scaling relations between velocity dispersion, complex size, gas mass,
and SFRs.

@@

Determining the multi-phase ISM properties of early galaxies
is a critical piece to understanding the evolution and
assembly history of galaxies, since they set the pace
for chemical reactions and excitation rates for the coolants in the ISM (and subsequent star formation).
Observations leveraging the combination of spatio-spectral imaging of
multi-band continuum and spectral line emission are crucial for better understanding
the role of \highz galaxy populations
(e.g., LBGs, BzKs, and DSFGs) in
galaxy evolution and the ISM physics behind their intense star formation in the early universe
(if only the ALMA TAC will give us to the time to do so)...
ngVLA.

@@

\appendix
\section{Schmidt-Kennicutt Relation}
As benchmarking, we check the SK relation for the MCs identified based on their SFR and gas surface densities.
We show in \Fig{sk} the MCs of \flower, identified using different $n_{\rm cut}$ in the ``accreting snapshot'' 
(see \Sec{sfh} for details) compared to those reported in \obs.

@@

\AP{I would put a figure with the SK-relation for the clumps in a single snapshot for different cuts, along with the observed points and the global \flower point from the data found in \citet{Pallottini17a}}
\DL{to do... after getting points from Pallo, then update plot\_cloud\_prop.py and plotsingleSS.py (uncomment plot\_suff(SK) and only plot snapshot 16)}

\begin{figure*}[htbp]
\centering
\includegraphics[trim=0 0 0 0, clip, width=0.85\textwidth]{\figpath/}
\caption{
SFR and gas surface densities of MCs identified in \flower in \ncode{serra} (star symbols) compared to those 
observed in 0\,$\lesssim$\,\z$\lesssim$\,2 galaxies.
Literature data are compiled from \citealt{Kennicutt98a, Bouche07a, Daddi10a, Daddi10b, Genzel10a, Tacconi10a} and 
\citealt{Pallottini17b}.
%The literature data are compiled from \citealt{Leroy13a, Genzel13a, Sharon13a, Hodge15a}, \citealt{Pallottini17b} 
%and references therein, and Sharon et al. in prep.
\label{fig:sk}}
\end{figure*}
